---
title: "Average User CA"
author: "Ariella Fuzaylov"
date: "3/28/2021"
output: pdf_document
---

```{r setup, include=FALSE}
library(ggplot2)
library(gridExtra)

library(tidyverse)
library(tm)
library(SnowballC)
library(textclean)
library(FactoMineR)
library(factoextra)
library("gplots")
library(corrplot)
library(dummy)
library(missMDA)
library(splitstackshape)
library(stats)
library(cluster)
```

## Loading Data From CSV and Update Header

```{r load data}
my.data=read.csv("Online Recipe Sharing.csv", header=TRUE)
colnames(my.data)<-c("Timestamp", "Age", "Primary.Meal.Prepper", "Household.Dietary.Restriction",
"Home.Cooking.Rate", 
"Primary.Recipe.Format", 
"Primary.Search.Website",
"Enjoyed.Website.Searching", "Comments.Enjoyed.Website.Searching", "NOT.Enjoyed.Website.Searching", "Comments.NOT.Enjoyed.Website.Searching", "Recipe.Search.Bar.Frequency", 
"Previous.Recipe.Search.Frequency",
"Browsing.While.Searching.Frequecny", 
"Click.Rate", 
"Search.Browse.Same.Websites",
"Primary.Browsing.Website", 
"Enjoyed.Website.Browsing", 
"Comments.Enjoyed.Website.Browsing", "NOT.Enjoyed.Website.Browsing", "Comments.NOT.Enjoyed.Website.Browsing", "Primary.Source.of.Reviews",
"Source.of.Influential.Reviews", "Frequency.Reviews.Effect.Behavior", 
"Frequency.Seek.Out.Review", 
"Frequency.of.Review", 
"Frequency.of.Recipe.Saving", 
"Method.of.Recipe.Saving", 
"Modification.Frequency", 
"Modification.Influence.Factors",
"Modification.Record.Frequency", 
"Modification.Record.Method", 
"Satisfaction.with.Available.Record.Methods", 
"Interest.in.Improved.Record.Method",
"Frequency.of.Recipe.Discussion", "Frequency.of.Reading.Discussion",
"Primary.Discussion.Medium", "Enjoyed.Features.of.Discussion.Mediums", "Ingredients.L.V.Above", 
"Ingredients.L.Comments.Inline.V.Below", "Ingredients.Above.Comments.Below.V.Inline", "Ingredients.By.Step.V.Above", 
"Ingredients.By.Step.V.Scroll.L", 
"Ingredients.Above.V.Scroll.L")

```

## Re-Factor Data

If Respondent indicated that they search and browse on the same websites, populate the empty cells with the same data. This assumes that the user's searching behavior is exactly the same as the browsing behavior if the user selected yes for searching and browsing on the same websites.

```{r fill in browsing blanks}
for (i in 1:nrow(my.data)){
  if (my.data$Search.Browse.Same.Websites[i]=="No"){
    my.data$Primary.Browsing.Website[i]<-my.data$Primary.Search.Website[i]
    my.data$Enjoyed.Website.Browsing[i]<-my.data$Enjoyed.Website.Searching[i]
    my.data$NOT.Enjoyed.Website.Browsing[i]<-my.data$NOT.Enjoyed.Website.Searching[i]
  }
}
```



Since the data set is small, I am consolidating some of the categories.

- Primary Meal Prepper will be Respondent if the individual taking the survey indicated that they are the primary meal prepper in their household or if they cook for themselves, and other in all other cases.

- Dietary restriction will become a yes or no question

- Home Cooking Rate will become Daily if the respondents cooks at home most days, weekly if the respondent cooks several times a week, and monthly is the respondent cooks a couple times a month.

```{r factoring}
my.data.factored<-my.data
my.data.factored$Age<-as.factor(my.data$Age)

my.data.factored$Primary.Meal.Prepper<-as.factor(my.data.factored$Primary.Meal.Prepper)

my.data.factored$Household.Dietary.Restriction<-as.factor(my.data.factored$Household.Dietary.Restriction)

my.data.factored$Home.Cooking.Rate<-as.factor(my.data.factored$Home.Cooking.Rate)

my.data.factored$Ingredients.L.V.Above<-as.factor(my.data.factored$Ingredients.L.V.Above)
my.data.factored$Ingredients.By.Step.V.Above<-as.factor(my.data.factored$Ingredients.By.Step.V.Above)
my.data.factored$Ingredients.Above.V.Scroll.L<-as.factor(my.data.factored$Ingredients.Above.V.Scroll.L)
my.data.factored$Ingredients.L.Comments.Inline.V.Below<-as.factor(my.data.factored$Ingredients.L.Comments.Inline.V.Below)
my.data.factored$Ingredients.By.Step.V.Scroll.L<-
  as.factor(my.data.factored$Ingredients.By.Step.V.Scroll.L)
my.data.factored$Ingredients.Above.Comments.Below.V.Inline<-
  as.factor(my.data.factored$Ingredients.Above.Comments.Below.V.Inline)
my.data.factored$Click.Rate<-as.factor(my.data.factored$Click.Rate)
my.data.factored$Search.Browse.Same.Websites<-as.factor(my.data.factored$Search.Browse.Same.Websites)
my.data.factored$Interest.in.Improved.Record.Method<-as.factor(my.data.factored$Interest.in.Improved.Record.Method)

my.data.factored<- mutate(my.data.factored, 
                          Age = fct_collapse(Age, 
                                             YA = c("18 - 24 years old","25 - 34 years old"),
                                             Adult = c("35 - 44 years old","45 - 54 years old","55 - 64 years old")),
                          Primary.Meal.Prepper = fct_collapse(Primary.Meal.Prepper,
                                                              Respondent = c("You", "I cook for myself"),
                                                              other_level = "Other"),
                  Household.Dietary.Restriction=fct_collapse(Household.Dietary.Restriction,
                                                             No="None",
                                                              other_level = "Yes"),
                  Home.Cooking.Rate=fct_collapse(Home.Cooking.Rate,
                                                 Daily=c("Almost every meal","Daily","Every meal"),
                                                 Weekly.or.Less=c("Several times a week","Once or twice a week","Once or twice a month")),
                  Ingredients.L.V.Above=fct_collapse(Ingredients.L.V.Above,
                                                     Ing.L =c("A"),
                                                     Ing.Above=("B"),
                                                     other_level = "EMPTY"),
                  Ingredients.By.Step.V.Above=fct_collapse(Ingredients.By.Step.V.Above,
                                                           Ing.By.Step=c("A"),
                                                           Ing.Abov=c("B"),
                                                     other_level = "EMPTY"),
                  Ingredients.Above.V.Scroll.L=fct_collapse(Ingredients.Above.V.Scroll.L,
                                                            Ing.Above=c("A"),
                                                            Scroll.L=c("B"),
                                                     other_level = "EMPTY"),
                  Ingredients.L.Comments.Inline.V.Below=fct_collapse(Ingredients.L.Comments.Inline.V.Below,
                                                                     Ing.L.Com.Inline=c("A"),
                                                                     Ing.L.Com.Below=c("B"),
                                                     other_level = "EMPTY"),
                  Ingredients.By.Step.V.Scroll.L=fct_collapse(Ingredients.By.Step.V.Scroll.L,
                                                              Ing.By.Step=c("A"),
                                                              Ing.Scroll=("B"),
                                                     other_level = "EMPTY"),
                  Ingredients.Above.Comments.Below.V.Inline=fct_collapse(Ingredients.Above.Comments.Below.V.Inline,
                                                                         Ing.Above.C.Below=c("A"),
                                                                         Ing.Above.C.Inline=c("B"),
                                                     other_level = "EMPTY"),
                  Click.Rate=fct_collapse(Click.Rate, "0 - 3" =c("0 - 3"),"4 - 7"=c("4 - 7") ,
                                           "8 - 11"=c("8 - 11"),  "16 - 19"=c("16 - 19")) ,
                  Search.Browse.Same.Websites=fct_collapse(Search.Browse.Same.Websites,Yes=c("Yes"), No= c("No")),
                  
                  Interest.in.Improved.Record.Method=fct_collapse(Interest.in.Improved.Record.Method,Yes=c("Yes"), No= c("No"))
                   
                  )
```
### Website Recoding:

For the sake of this analysis any website that has a test kitchen that creates editorial content or is able to curate content from professional sources is a magazine, a a website with one or two people testing recipes is a blog, and a website that allows users to contribute their own recipes is community based. The information for this classification is found on the website's about page. Additionally, media such as cookbooks and podcasts are classified under Influencers due to their personality driven nature.

### Discussion Method Recoding:

Any type of online chatting be it texting, discord, etc. has been grouped together into Digital Chat. Any type of interpersonal communication where a chat method was not specified is grouped into verbal. 

Note saving methods that mention remembering or memory are grouped into memory, while respondents that indicate that they do not take any type of notes and do not try to remember are group are grouped into None.

### Modification Recoding:

Modification influence factors pertaining to diet, or nutrition are grouped together under the umbrella of "Diet".

Modification influence factors pertaining to personal preference for food, flavor, or preparation method are grouped together under the category of "Personal Preference.

Modification influence factors pertaining ingredients availability are grouped together under the category of "Ing. Availability"

```{r create cleaning vector}
unique(separate_rows(my.data.factored[32],1, sep = ";"))
my.data.selected<-my.data.factored[c(6,7,8,10,17,18,20,22,23,28,37,30,32,38)]
variables<-c()

##This creates a vector that will recode the variables with the proper names
 for (i in 1:ncol(my.data.selected)){
  temp<- my.data.selected[i]
  temp<-separate_rows(temp,1, sep = ";")
  variables<-append(variables,temp[[1]])
  variables<-unique(variables)
  data.frame(variables)
 }

variables

cleaned.variables<-c(
  "Mobile",
  "Desktop",
  "Digital",
  "Physical Print",
  "Physical Print",
  "Digital",
  "Physical Family",
  "Physical Family",
  "Physical Family",
  "Physical Family",
  "Mags",
  "Blogs",
  "Google",
  #"Youtube",
  "Video",
  "Community Based" ,
  "Mags",
  "Community Based" ,
  "Pinterest",
  "Blogs",
  # "TikTok",
  "Video",
  "Mags",
  "Facebook",
  "Reddit",
  "Mags",
  "Mags",
  "Mags",
  "Mags",
  "Instagram",
  "Mags",
  "Friends/Family",
  "Blogs",
  "NA",
  "Blogs",
  "Mags",
  "Instagram",
  "Instagram",
  "None",
  "None",
  "Friends/Family",
  "Online Groups",
  "Other Users",
  "Influencers",
  "Influencers",
  "Facebook",
  "Browser Bookmarks",
  "Digital Filing",
  "Memory",
  "Search History",
  "Save Function",
  "Physical Filing",
  "None",
  "Memory",
  "Memory",
  "Memory",
  "Save Function",
  "Verbal",
  "Verbal",
  "Verbal",
  "Digital Chat",
  "Verbal",
  "Verbal",
  "Digital Chat",
  "Google Docs",
  "Digital Chat",
  "Verbal",
  "Verbal",
  "Verbal",
  "Verbal",
  "Verbal",
  "Verbal",
  "Verbal",
  "Verbal",
  "Digital Chat",
  "None",
  "Digital Chat",
  "Verbal",
  "Digital Chat",
  "Digital Chat",
  "None",
  "Diet",
  "Diet",
  "Preference",
  "Diet",
  "Ing. Availability",
  "Ing. Availability",
  "Recommendation",
  "Preference",
  "Memory",
  "Digital",
  "Physical",
  "Memory",
  "None",
  "Comments",
  "None",
  "Memory",
  "Memory",
  "None",
  "None",
  "Memory",
  "None",
  "None",
  "5 Star Review",
  "Groups",
  "Up/Down Vote Posts",
  "Up/Down Vote Com.",
  "Collapse Comment",
  "Comment Reply",
  "Comment Thread",
  "Inline Comment")

names(cleaned.variables)<-variables
```
## Functions for Cleaning Data


```{r dummies}

dummies<-function(search.data, to.clean){
  col.names<-c(names(search.data))
  col.names<-col.names[col.names!=to.clean]
  search.data.clean<- search.data%>% separate_rows(all_of(to.clean), sep = ";")
  
  search.data.clean[to.clean]<-
    as.character(cleaned.variables[search.data.clean[[to.clean]]])
  search.data.clean[to.clean]<-lapply(search.data.clean[to.clean],function(x) replace(x,is.na(x),"Empty"))
  
  search.data.dummies<-search.data.clean%>%
    select((to.clean))%>%
    dummy()%>%
    bind_cols(search.data.clean)%>%
    select(-(to.clean))%>%
    pivot_longer(cols=-col.names, names_to = "key", values_to = "value")%>%
    filter(value!=0)
  
  search.data.dummies<-search.data.dummies%>%
    unique()
  
  search.data.dummies<-search.data.dummies%>%
    spread(key, value, fill = 0)
    
}

```


## Load Factored Data
```{r load factored data and clean}
search.data<-my.data.factored[-c(1,9,11,19,21)]

search.data<-data.frame(search.data)
new.names=c("Age", "Meal.Prepper","Dietary.Restriction","Home.Cook.Rate","Primary.Format.C","Primary.S.C",
            "Enjoyed.S.C","NOT.Enjoyed.S.C","Recipe.Search.F","Repeat.S.F","Browse.Search.F","Click.Rate",
            "Search.Browse.Same","Primary.B.C","Enjoyed.B.C","NOT.Enjoyed.B.C", "Primary.R.C", "Influential.R.C",
            "Use.R.F","Seek.R.F", "R.F","Save.F","Save.C","Mod.F","Why.Mod.C", "Mod.Note.F", "Mod.Note.C",
            "Note.Method.S","Potential.Note.Taker","Disc.F","Read.Disc.F","Disc.C","Enjoy.Disc.C", "Ing.L.V.Above",
            "Ing.L.Com.Inline.V.Below","Ing.Above.Com.Below.V.Inline",  "Ing.By.Step.V.Above",  "Ing.By.Step.V.Scroll.L",
            "Ing.Above.V.Scroll.L"
            )
colnames(search.data)<-new.names

```


```{r MCA with dummies}
cleaned<-search.data
to.dummy<-select(cleaned, ends_with(".C"))
to.dummy.cols<-c(colnames(to.dummy))
for (col in to.dummy.cols){
   cleaned<-dummies(cleaned,c(col))
  
}

cleaned<-data.frame(cleaned)
to.num<-grepl(".C_",colnames(cleaned))
cleaned[to.num]<-as.integer(unlist(cleaned[to.num]))

```

```{r}
cleaned[names(select(cleaned, ends_with(".F")))][is.na(cleaned[names(select(cleaned, ends_with(".F")))])]<-0

# aggregate(select(cleaned, where(is.numeric)), by=list(cleaned$Age,cleaned$Meal.Prepper,cleaned$Dietary.Restriction,cleaned$Home.Cook.Rate), FUN=sum)%>% select(!ends_with((".F")))

aggregate(select(cleaned, ends_with(".F")), by=list(cleaned$Meal.Prepper,cleaned$Dietary.Restriction,cleaned$Home.Cook.Rate), FUN=mean)
```

```{r isolate frequent users}
#isolate frequent users
cleaned<- filter(cleaned, Home.Cook.Rate!="Monthly")

#REMOVE USERS WHO DID NOT COMPLETE ab TEST
cleaned<-filter(cleaned, Ing.L.Com.Inline.V.Below!="EMPTY")


```

```{r}

cleaned.f<-cleaned


## construct dendrograms
hc.complete =hclust (dist(cleaned.f), method ="complete")

gower.dist <- daisy(cleaned.f, metric = c("gower"))

##plot dendrograms and groups
divisive.clust <- diana(as.matrix(gower.dist), 
                  diss = TRUE, keep.diss = TRUE)
plot(divisive.clust, main = "Divisive")
rect.hclust(divisive.clust,k=2)
all.gower.g<-cutree(divisive.clust,k=2)
all.gower<-mutate(cleaned.f, cluster=as.factor(all.gower.g))


plot(hc.complete ,main =" Complete Linkage ", xlab="", sub ="",
cex =.9)
rect.hclust(hc.complete,k=2)
all.complete.g<-cutree(hc.complete, k=2)
all.complete<-mutate(cleaned.f, cluster=as.factor(all.complete.g))


```

```{r}

for (f in names(select(all.complete, ends_with(".F")))){
  p<-ggplot(all.complete, aes(x=cluster, fill=cluster))+
    geom_boxplot(aes_string(y=f))
  print(p)
}


```

Cluster 2 contains respondents who on average more frequently interact with recipes.

```{r}

for (f in names(select(all.gower, ends_with(".F")))){
  p<-ggplot(all.gower, aes(x=cluster, fill=cluster))+
    geom_boxplot(aes_string(y=f))
  print(p)
}


```

The Gower distance does not divide the users by recipe interaction frequency.

```{r}

for (f in names(select(cleaned, ends_with(".F")))){
  p<-ggplot(cleaned, aes(x=Meal.Prepper, fill=Dietary.Restriction))+
    geom_boxplot(aes_string(y=f))#+
    # facet_grid(~Dietary.Restriction)
  print(p)
}
```
```{r}

ggplot(all.complete,aes( x=Potential.Note.Taker))+
    geom_bar(aes(fill=cluster), position = "fill")+
    theme(axis.text.x = element_text(angle = 90))

for (i in names(select(all.complete, starts_with("Ing.")))){
  p<-ggplot(all.complete,aes( x=cluster))+
    geom_bar(aes_string(fill=i), position = "fill")+
    theme(axis.text.x = element_text(angle = 90))
  
  print(p)
}
```

Since cluster two represents a group of users who interacts with recipes more frequentlly than group one, I will weight their responses higher than cluster one.
# Results:

## Ingredients Listed Left vs. Above:
Ingredients left

## (Given Ingredients Left) Comments Inline vs. Below:
Comments inline

## (Given Ingredients Above) Comments Below vs. Inline:
Comments inline

## Ingredients Listed Step by Step vs. Above:
Ingredients listed step by step

## Ingredients Listed Step by Step vs. Pinned Left While Scrolling: 
Ingredients listed step by step

- Ingredients listed step by step is overall the most liked

## Ingredients Listed Above vs. Pinned Left While Scrolling:
Ingredients pinned left while scrolling

The overall recipe view most enjoyed by users is ingredients pinned left while scrolling with comments inline.

The in use recipe view most enjoyed by users is ingredients listed step by step.


```{r}
for (i in names(select(cleaned, starts_with("Ing.")))){
  p<-ggplot(cleaned,aes( fill=Potential.Note.Taker))+
    geom_bar(aes_string(x=i))+
    theme(axis.text.x = element_text(angle = 90))
  
  print(p)
}
```

```{r}
note.takers<-filter(cleaned, Potential.Note.Taker == "Yes")
for (i in names(select(note.takers, starts_with("Ing.")))){
  p<-ggplot(note.takers,aes_string( fill=i))+
    geom_bar(aes(x=Dietary.Restriction))
  
  print(p)
}
```

```{r}

hc.complete =hclust (dist(note.takers), method ="complete")
hc.average =hclust (dist(note.takers), method ="average")
gower.dist <- daisy(note.takers, metric = c("gower"))


divisive.clust <- diana(as.matrix(gower.dist), 
                  diss = TRUE, keep.diss = TRUE)

plot(divisive.clust, main = "Divisive")
rect.hclust(divisive.clust,k=3)

plot(hc.complete ,main =" Complete Linkage ", xlab="", sub ="",
cex =.9)
rect.hclust(hc.complete,k=3)
plot(hc.average , main =" Average Linkage ", xlab="", sub ="",
cex =.9)
rect.hclust(hc.average,k=3)

```

```{r}
format<-select(cleaned, starts_with("Primary.Format.C_"))%>% 
  gather(Var, Val) %>% 
  count(Var, Val)%>%
  filter(Val == 1)
ggplot(format)+
    geom_col(aes(x=Var, y=n, fill = Var))+
    theme(axis.text.x = element_text(angle = 90))
filter(all.complete, cluster==2)%>%count()
format.c2<-filter(all.complete, cluster==2)%>%
  select(starts_with("Primary.Format.C_"))%>% 
  gather(Var, Val) %>% 
  count(Var, Val)%>%
  filter(Val == 1)
format.c2
ggplot(format.c2)+
    geom_col(aes(x=Var, y=n, fill = Var))+
    theme(axis.text.x = element_text(angle = 90))
```

The primary format used by 40/58 respondents is mobile. When looking at cluster two from complete linkage clustering on all the respondents we find that 21/27 respondents primarily interact with recipes on mobile.